### 2025-03-23 plots/elision/mem_summary.tex
Flesh out summaries for experiments in section 9

\begin{tabular}{lrr}
\toprule
configuration & elision-naive & elision-opt \\
suite &  &  \\
\midrule
\binarytrees & 1.06MiB \footnotesize{± 22.22KiB} & 1.06MiB \footnotesize{± 24.18KiB} \\
\regexredux & 74.37MiB \footnotesize{± 3.15MiB} & 72.76MiB \footnotesize{± 3.78MiB} \\
\somrsast & 1.16MiB \footnotesize{± 517.62KiB} & 1.22MiB \footnotesize{± 1.20MiB} \\
\somrsbc & 763.30KiB \footnotesize{± 312.94KiB} & 692.14KiB \footnotesize{± 370.14KiB} \\
\yksom & 926.88KiB \footnotesize{± 189.68KiB} & 1.37MiB \footnotesize{± 160.51KiB} \\
\bottomrule
\end{tabular}

### 2025-03-23 plots/premopt/mem_summary.tex
Flesh out summaries for experiments in section 9

\begin{tabular}{lrrr}
\toprule
configuration & premopt-naive & premopt-none & premopt-opt \\
suite &  &  &  \\
\midrule
\binarytrees & 1.06MiB \footnotesize{± 18.74KiB} & 1.06MiB \footnotesize{± 16.18KiB} & 1.06MiB \footnotesize{± 26.75KiB} \\
\regexredux & 73.57MiB \footnotesize{± 3.46MiB} & 72.60MiB \footnotesize{± 3.05MiB} & 73.25MiB \footnotesize{± 3.35MiB} \\
\somrsast & 1.22MiB \footnotesize{± 1.21MiB} & 1.23MiB \footnotesize{± 1.08MiB} & 1.22MiB \footnotesize{± 1.15MiB} \\
\somrsbc & 694.50KiB \footnotesize{± 347.61KiB} & 689.14KiB \footnotesize{± 330.27KiB} & 701.91KiB \footnotesize{± 372.72KiB} \\
\yksom & 1.38MiB \footnotesize{± 165.17KiB} & 1.37MiB \footnotesize{± 161.23KiB} & 1.37MiB \footnotesize{± 153.53KiB} \\
\bottomrule
\end{tabular}

### 2025-03-26 plots/elision/mem_summary.tex
First complete(ish) draft of the evaluation section.
Put the correct elision mem data in table 6

@@
-\begin{tabular}{lrr}
+\begin{tabular}{lrrrrrrr}
 \toprule
-configuration & elision-naive & elision-opt \\
+configuration & Elision Naive & Elision Opt \\
 suite &  &  \\
 \midrule
-\binarytrees & 1.06MiB \footnotesize{± 22.22KiB} & 1.06MiB \footnotesize{± 24.18KiB} \\
-\regexredux & 74.37MiB \footnotesize{± 3.15MiB} & 72.76MiB \footnotesize{± 3.78MiB} \\
-\somrsast & 1.16MiB \footnotesize{± 517.62KiB} & 1.22MiB \footnotesize{± 1.20MiB} \\
-\somrsbc & 763.30KiB \footnotesize{± 312.94KiB} & 692.14KiB \footnotesize{± 370.14KiB} \\
-\yksom & 926.88KiB \footnotesize{± 189.68KiB} & 1.37MiB \footnotesize{± 160.51KiB} \\
+\binarytrees & 1.07MiB \footnotesize{(1.05MiB-1.09MiB)} & 1.06MiB \footnotesize{(1.04MiB-1.09MiB)} \\
+\regexredux & 75.35MiB \footnotesize{(72.13MiB-78.58MiB)} & 74.19MiB \footnotesize{(70.88MiB-77.50MiB)} \\
+\midrule
+\alacritty & 8.69MiB \footnotesize{(8.23MiB-9.18MiB)} & 8.65MiB \footnotesize{(8.20MiB-9.14MiB)} \\
+\fd & 3.51MiB \footnotesize{(3.50MiB-3.53MiB)} & 3.51MiB \footnotesize{(3.49MiB-3.52MiB)} \\
+\grmtools & 11.71MiB \footnotesize{(11.58MiB-11.84MiB)} & 60.08MiB \footnotesize{(59.42MiB-60.75MiB)} \\
+\ripgrep & 5.22MiB \footnotesize{(5.19MiB-5.24MiB)} & 7.71MiB \footnotesize{(7.66MiB-7.76MiB)} \\
+\midrule
+\somrsast & 1.14MiB \footnotesize{(1.14MiB-1.15MiB)} & 1.08MiB \footnotesize{(1.08MiB-1.09MiB)} \\
+\somrsbc & 740.48KiB \footnotesize{(736.99KiB-743.99KiB)} & 629.92KiB \footnotesize{(624.19KiB-635.70KiB)} \\
+\yksom & 931.19KiB \footnotesize{(927.32KiB-935.07KiB)} & 1.28MiB \footnotesize{(1.27MiB-1.29MiB)} \\
 \bottomrule

### 2025-06-26 plots/premopt_summary.tex
Flesh out summary results table for premature finalizer prevention opt. with som-rs results

\begin{tabular}{l l r@{\hspace{0.5em}}l r@{\hspace{0.5em}}l}
\toprule
Suite & Configuration & \multicolumn{2}{c}{WALLCLOCK} & \multicolumn{2}{c}{USER} \\
\midrule
som-rs-ast & som-rs-ast-premopt-none & \textbf{817.76} & \scriptsize\textcolor{gray!80}{[781.48, 855.74]} & \textbf{809.55} & \scriptsize\textcolor{gray!80}{[773.30, 847.51]} \\
 & som-rs-ast-default & 1.01×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.95, 1.08]} & 1.01×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.96, 1.09]} \\
 & som-rs-ast-premopt-naive & 1.01×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.95, 1.07]} & 1.00×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.95, 1.07]} \\
\midrule
som-rs-bc & som-rs-bc-premopt-none & \textbf{237.93} & \scriptsize\textcolor{gray!80}{[226.62, 249.81]} & \textbf{234.58} & \scriptsize\textcolor{gray!80}{[223.28, 246.46]} \\
 & som-rs-bc-default & 1.05×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.99, 1.13]} & 1.06×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.99, 1.13]} \\
 & som-rs-bc-premopt-naive & 1.01×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.94, 1.08]} & 1.01×\textsuperscript{\dag} & \scriptsize\textcolor{gray!80}{[0.94, 1.08]} \\
\bottomrule
\end{tabular}

### 2025-07-16 tables/gcvs_perf_individual.tex
Add final layout of GCVS experiment appendix perf section

\begin{tabular}{l l @{\hspace{6pt}}r@{\hspace{3pt}}l @{\hspace{6pt}}r@{\hspace{3pt}}l @{\hspace{6pt}}r@{\hspace{3pt}}l @{\hspace{6pt}}r@{\hspace{3pt}}l @{\hspace{6pt}}r@{\hspace{3pt}}l @{\hspace{6pt}}r@{\hspace{3pt}}l}
\toprule
Suite & Benchmark & \multicolumn{6}{c}{Wallclock-time (seconds)} & \multicolumn{6}{c}{User-time (seconds)} \\
 &  & \multicolumn{2}{c}{RC \texttt{[jemalloc]}} & \multicolumn{2}{c}{Alloy \texttt{[default]}} & \multicolumn{2}{c}{RC \texttt{[gcmalloc]}} & \multicolumn{2}{c}{RC \texttt{[jemalloc]}} & \multicolumn{2}{c}{Alloy \texttt{[default]}} & \multicolumn{2}{c}{RC \texttt{[gcmalloc]}} \\
\midrule
\multirow{10}{*}{\rotatebox{90}{alacritty}} & Cur. Motion & 0.65 & \scriptsize\textcolor{gray!60}{[0.63,0.66]} & 0.66 & \scriptsize\textcolor{gray!60}{[0.65,0.66]} & 0.66 & \scriptsize\textcolor{gray!60}{[0.65,0.67]} & 1.08 & \scriptsize\textcolor{gray!60}{[1.03,1.14]} & 1.09 & \scriptsize\textcolor{gray!60}{[1.04,1.13]} & 1.09 & \scriptsize\textcolor{gray!60}{[1.05,1.13]} \\
 & Dense Cells & 2.16 & \scriptsize\textcolor{gray!60}{[2.14,2.19]} & 2.16 & \scriptsize\textcolor{gray!60}{[2.14,2.18]} & 2.14 & \scriptsize\textcolor{gray!60}{[2.10,2.18]} & 6.66 & \scriptsize\textcolor{gray!60}{[6.53,6.79]} & 6.62 & \scriptsize\textcolor{gray!60}{[6.51,6.74]} & 6.58 & \scriptsize\textcolor{gray!60}{[6.43,6.73]} \\
 & Light Cells & 0.37 & \scriptsize\textcolor{gray!60}{[0.36,0.38]} & 0.37 & \scriptsize\textcolor{gray!60}{[0.36,0.39]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.37,0.38]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.31,0.37]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.31,0.37]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.30,0.37]} \\
 & Scroll & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.27]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.24,0.28]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.25,0.28]} & 0.11 & \scriptsize\textcolor{gray!60}{[0.10,0.12]} & 0.11 & \scriptsize\textcolor{gray!60}{[0.10,0.13]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.10,0.13]} \\
 & Scroll Btm & 0.32 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} & 0.32 & \scriptsize\textcolor{gray!60}{[0.31,0.33]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.15]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.15]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.15]} \\
 & Scroll Btm
(small) & 0.32 & \scriptsize\textcolor{gray!60}{[0.31,0.33]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} & 0.32 & \scriptsize\textcolor{gray!60}{[0.31,0.34]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.16]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.14,0.16]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.16]} \\
 & Scroll
(fullscreen) & 0.38 & \scriptsize\textcolor{gray!60}{[0.37,0.38]} & 0.39 & \scriptsize\textcolor{gray!60}{[0.38,0.40]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.37,0.39]} & 0.24 & \scriptsize\textcolor{gray!60}{[0.22,0.26]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.25,0.30]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.20,0.25]} \\
 & Scroll Top & 0.25 & \scriptsize\textcolor{gray!60}{[0.23,0.26]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.24,0.28]} & 0.24 & \scriptsize\textcolor{gray!60}{[0.22,0.26]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.10,0.13]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.10,0.14]} & 0.11 & \scriptsize\textcolor{gray!60}{[0.09,0.12]} \\
 & Scroll Top
(small) & 0.32 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} & 0.32 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.15]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.14,0.15]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.14,0.16]} \\
 & Unicode & 0.23 & \scriptsize\textcolor{gray!60}{[0.21,0.24]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.28]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.25,0.28]} & 0.10 & \scriptsize\textcolor{gray!60}{[0.09,0.12]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.11,0.14]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.11,0.13]} \\
\midrule
\multirow{7}{*}{\rotatebox{90}{fd}} & Cmd Exec. & 1.29 & \scriptsize\textcolor{gray!60}{[1.27,1.30]} & 1.28 & \scriptsize\textcolor{gray!60}{[1.27,1.30]} & 1.29 & \scriptsize\textcolor{gray!60}{[1.27,1.30]} & 1.05 & \scriptsize\textcolor{gray!60}{[1.04,1.07]} & 1.12 & \scriptsize\textcolor{gray!60}{[1.10,1.13]} & 1.12 & \scriptsize\textcolor{gray!60}{[1.11,1.14]} \\
 & Cmd Exec.
(large output) & 1.24 & \scriptsize\textcolor{gray!60}{[1.23,1.25]} & 1.25 & \scriptsize\textcolor{gray!60}{[1.22,1.28]} & 1.26 & \scriptsize\textcolor{gray!60}{[1.24,1.27]} & 1.02 & \scriptsize\textcolor{gray!60}{[1.01,1.04]} & 1.10 & \scriptsize\textcolor{gray!60}{[1.07,1.13]} & 1.11 & \scriptsize\textcolor{gray!60}{[1.10,1.13]} \\
 & File Extension & 0.13 & \scriptsize\textcolor{gray!60}{[0.13,0.13]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.14,0.16]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.13,0.14]} & 0.04 & \scriptsize\textcolor{gray!60}{[0.03,0.04]} & 0.04 & \scriptsize\textcolor{gray!60}{[0.04,0.05]} & 0.04 & \scriptsize\textcolor{gray!60}{[0.03,0.04]} \\
 & File Type & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.13,0.14]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.03 & \scriptsize\textcolor{gray!60}{[0.02,0.04]} & 0.04 & \scriptsize\textcolor{gray!60}{[0.03,0.04]} & 0.04 & \scriptsize\textcolor{gray!60}{[0.03,0.04]} \\
 & No Pattern & 0.18 & \scriptsize\textcolor{gray!60}{[0.18,0.19]} & 0.29 & \scriptsize\textcolor{gray!60}{[0.27,0.31]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.21,0.23]} & 0.16 & \scriptsize\textcolor{gray!60}{[0.15,0.17]} & 0.29 & \scriptsize\textcolor{gray!60}{[0.27,0.30]} & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.25]} \\
 & Simple & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.32,0.34]} & 0.32 & \scriptsize\textcolor{gray!60}{[0.31,0.32]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.15]} & 0.18 & \scriptsize\textcolor{gray!60}{[0.17,0.19]} & 0.16 & \scriptsize\textcolor{gray!60}{[0.15,0.17]} \\
 & Simple (-HI) & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.14,0.15]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.13,0.13]} & 0.03 & \scriptsize\textcolor{gray!60}{[0.02,0.03]} & 0.04 & \scriptsize\textcolor{gray!60}{[0.03,0.04]} & 0.04 & \scriptsize\textcolor{gray!60}{[0.03,0.04]} \\
\midrule
\multirow{4}{*}{\rotatebox{90}{grmtools}} & Eclipse & 3.48 & \scriptsize\textcolor{gray!60}{[3.46,3.51]} & 3.44 & \scriptsize\textcolor{gray!60}{[3.41,3.48]} & 3.74 & \scriptsize\textcolor{gray!60}{[3.70,3.78]} & 3.32 & \scriptsize\textcolor{gray!60}{[3.29,3.35]} & 3.28 & \scriptsize\textcolor{gray!60}{[3.24,3.31]} & 3.59 & \scriptsize\textcolor{gray!60}{[3.55,3.64]} \\
 & Hadoop & 2.86 & \scriptsize\textcolor{gray!60}{[2.85,2.87]} & 2.92 & \scriptsize\textcolor{gray!60}{[2.91,2.93]} & 3.09 & \scriptsize\textcolor{gray!60}{[3.08,3.10]} & 2.77 & \scriptsize\textcolor{gray!60}{[2.76,2.78]} & 2.80 & \scriptsize\textcolor{gray!60}{[2.79,2.81]} & 2.99 & \scriptsize\textcolor{gray!60}{[2.98,3.00]} \\
 & Jenkins & 2.90 & \scriptsize\textcolor{gray!60}{[2.90,2.91]} & 2.99 & \scriptsize\textcolor{gray!60}{[2.94,3.04]} & 3.02 & \scriptsize\textcolor{gray!60}{[3.01,3.03]} & 2.74 & \scriptsize\textcolor{gray!60}{[2.73,2.75]} & 2.81 & \scriptsize\textcolor{gray!60}{[2.77,2.84]} & 2.90 & \scriptsize\textcolor{gray!60}{[2.89,2.91]} \\
 & Spring & 2.43 & \scriptsize\textcolor{gray!60}{[2.42,2.43]} & 2.51 & \scriptsize\textcolor{gray!60}{[2.51,2.52]} & 2.63 & \scriptsize\textcolor{gray!60}{[2.61,2.65]} & 2.35 & \scriptsize\textcolor{gray!60}{[2.35,2.36]} & 2.40 & \scriptsize\textcolor{gray!60}{[2.39,2.41]} & 2.54 & \scriptsize\textcolor{gray!60}{[2.53,2.56]} \\
\midrule
\multirow{13}{*}{\rotatebox{90}{ripgrep}} & Alternates & 1.18 & \scriptsize\textcolor{gray!60}{[1.18,1.19]} & 1.29 & \scriptsize\textcolor{gray!60}{[1.28,1.31]} & 1.21 & \scriptsize\textcolor{gray!60}{[1.20,1.22]} & 0.42 & \scriptsize\textcolor{gray!60}{[0.40,0.44]} & 0.51 & \scriptsize\textcolor{gray!60}{[0.49,0.53]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.41,0.44]} \\
 & Alternates
(no-case) & 1.31 & \scriptsize\textcolor{gray!60}{[1.30,1.31]} & 1.42 & \scriptsize\textcolor{gray!60}{[1.41,1.43]} & 1.33 & \scriptsize\textcolor{gray!60}{[1.33,1.34]} & 0.54 & \scriptsize\textcolor{gray!60}{[0.51,0.56]} & 0.65 & \scriptsize\textcolor{gray!60}{[0.63,0.67]} & 0.57 & \scriptsize\textcolor{gray!60}{[0.55,0.58]} \\
 & Literal & 1.12 & \scriptsize\textcolor{gray!60}{[1.11,1.12]} & 1.23 & \scriptsize\textcolor{gray!60}{[1.22,1.25]} & 1.15 & \scriptsize\textcolor{gray!60}{[1.14,1.15]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.32,0.35]} & 0.44 & \scriptsize\textcolor{gray!60}{[0.43,0.46]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.35,0.38]} \\
 & Literal
(no-case) & 1.19 & \scriptsize\textcolor{gray!60}{[1.19,1.19]} & 1.27 & \scriptsize\textcolor{gray!60}{[1.26,1.29]} & 1.20 & \scriptsize\textcolor{gray!60}{[1.20,1.21]} & 0.41 & \scriptsize\textcolor{gray!60}{[0.40,0.43]} & 0.50 & \scriptsize\textcolor{gray!60}{[0.48,0.52]} & 0.44 & \scriptsize\textcolor{gray!60}{[0.43,0.46]} \\
 & mmap
(no-case) & 1.67 & \scriptsize\textcolor{gray!60}{[1.66,1.68]} & 1.80 & \scriptsize\textcolor{gray!60}{[1.78,1.81]} & 1.72 & \scriptsize\textcolor{gray!60}{[1.71,1.72]} & 0.48 & \scriptsize\textcolor{gray!60}{[0.46,0.49]} & 0.58 & \scriptsize\textcolor{gray!60}{[0.56,0.60]} & 0.50 & \scriptsize\textcolor{gray!60}{[0.48,0.52]} \\
 & Literal
(default) & 1.08 & \scriptsize\textcolor{gray!60}{[1.07,1.09]} & 1.19 & \scriptsize\textcolor{gray!60}{[1.18,1.20]} & 1.10 & \scriptsize\textcolor{gray!60}{[1.10,1.11]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.32]} & 0.40 & \scriptsize\textcolor{gray!60}{[0.39,0.41]} & 0.32 & \scriptsize\textcolor{gray!60}{[0.31,0.33]} \\
 & mmap & 1.64 & \scriptsize\textcolor{gray!60}{[1.63,1.64]} & 1.75 & \scriptsize\textcolor{gray!60}{[1.74,1.77]} & 1.67 & \scriptsize\textcolor{gray!60}{[1.67,1.68]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.41,0.45]} & 0.52 & \scriptsize\textcolor{gray!60}{[0.50,0.54]} & 0.46 & \scriptsize\textcolor{gray!60}{[0.44,0.47]} \\
 & Literal
(Regex) & 1.13 & \scriptsize\textcolor{gray!60}{[1.12,1.14]} & 1.25 & \scriptsize\textcolor{gray!60}{[1.24,1.26]} & 1.15 & \scriptsize\textcolor{gray!60}{[1.15,1.16]} & 0.35 & \scriptsize\textcolor{gray!60}{[0.33,0.36]} & 0.44 & \scriptsize\textcolor{gray!60}{[0.43,0.46]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.35,0.38]} \\
 & UTF Greek & 3.29 & \scriptsize\textcolor{gray!60}{[3.28,3.30]} & 3.41 & \scriptsize\textcolor{gray!60}{[3.39,3.42]} & 3.33 & \scriptsize\textcolor{gray!60}{[3.32,3.33]} & 2.55 & \scriptsize\textcolor{gray!60}{[2.53,2.57]} & 2.64 & \scriptsize\textcolor{gray!60}{[2.62,2.66]} & 2.58 & \scriptsize\textcolor{gray!60}{[2.55,2.61]} \\
 & UTF Greek
(no-case) & 3.30 & \scriptsize\textcolor{gray!60}{[3.29,3.31]} & 3.42 & \scriptsize\textcolor{gray!60}{[3.39,3.44]} & 3.33 & \scriptsize\textcolor{gray!60}{[3.32,3.34]} & 2.56 & \scriptsize\textcolor{gray!60}{[2.53,2.59]} & 2.66 & \scriptsize\textcolor{gray!60}{[2.63,2.69]} & 2.56 & \scriptsize\textcolor{gray!60}{[2.53,2.58]} \\
 & UTF Word & 1.09 & \scriptsize\textcolor{gray!60}{[1.08,1.10]} & 1.21 & \scriptsize\textcolor{gray!60}{[1.20,1.22]} & 1.14 & \scriptsize\textcolor{gray!60}{[1.13,1.14]} & 0.35 & \scriptsize\textcolor{gray!60}{[0.33,0.37]} & 0.42 & \scriptsize\textcolor{gray!60}{[0.40,0.43]} & 0.37 & \scriptsize\textcolor{gray!60}{[0.36,0.39]} \\
 & UTF Word
(alt.) & 1.11 & \scriptsize\textcolor{gray!60}{[1.10,1.11]} & 1.21 & \scriptsize\textcolor{gray!60}{[1.20,1.22]} & 1.13 & \scriptsize\textcolor{gray!60}{[1.13,1.14]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.32,0.35]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.41,0.45]} & 0.35 & \scriptsize\textcolor{gray!60}{[0.33,0.36]} \\
 & Word & 1.12 & \scriptsize\textcolor{gray!60}{[1.11,1.12]} & 1.22 & \scriptsize\textcolor{gray!60}{[1.21,1.24]} & 1.14 & \scriptsize\textcolor{gray!60}{[1.13,1.14]} & 0.35 & \scriptsize\textcolor{gray!60}{[0.34,0.37]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.42,0.45]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.35,0.37]} \\
\midrule
\multirow{26}{*}{\rotatebox{90}{som-rs-ast}} & Bounce & 0.62 & \scriptsize\textcolor{gray!60}{[0.62,0.62]} & 0.96 & \scriptsize\textcolor{gray!60}{[0.94,0.98]} & 0.80 & \scriptsize\textcolor{gray!60}{[0.79,0.80]} & 0.62 & \scriptsize\textcolor{gray!60}{[0.61,0.62]} & 0.96 & \scriptsize\textcolor{gray!60}{[0.94,0.97]} & 0.79 & \scriptsize\textcolor{gray!60}{[0.79,0.79]} \\
 & BubbleSort & 0.56 & \scriptsize\textcolor{gray!60}{[0.56,0.57]} & 0.84 & \scriptsize\textcolor{gray!60}{[0.83,0.85]} & 0.71 & \scriptsize\textcolor{gray!60}{[0.71,0.72]} & 0.56 & \scriptsize\textcolor{gray!60}{[0.55,0.56]} & 0.83 & \scriptsize\textcolor{gray!60}{[0.82,0.84]} & 0.71 & \scriptsize\textcolor{gray!60}{[0.71,0.71]} \\
 & DeltaBlue & 0.77 & \scriptsize\textcolor{gray!60}{[0.77,0.78]} & 1.09 & \scriptsize\textcolor{gray!60}{[1.08,1.10]} & 0.98 & \scriptsize\textcolor{gray!60}{[0.98,0.98]} & 0.77 & \scriptsize\textcolor{gray!60}{[0.76,0.77]} & 1.07 & \scriptsize\textcolor{gray!60}{[1.06,1.08]} & 0.97 & \scriptsize\textcolor{gray!60}{[0.97,0.98]} \\
 & Dispatch & 0.59 & \scriptsize\textcolor{gray!60}{[0.58,0.60]} & 0.97 & \scriptsize\textcolor{gray!60}{[0.97,0.97]} & 0.77 & \scriptsize\textcolor{gray!60}{[0.76,0.77]} & 0.59 & \scriptsize\textcolor{gray!60}{[0.58,0.59]} & 0.96 & \scriptsize\textcolor{gray!60}{[0.96,0.97]} & 0.76 & \scriptsize\textcolor{gray!60}{[0.75,0.77]} \\
 & Fannkuch & 0.65 & \scriptsize\textcolor{gray!60}{[0.64,0.65]} & 1.01 & \scriptsize\textcolor{gray!60}{[0.95,1.07]} & 0.81 & \scriptsize\textcolor{gray!60}{[0.80,0.81]} & 0.64 & \scriptsize\textcolor{gray!60}{[0.64,0.65]} & 0.98 & \scriptsize\textcolor{gray!60}{[0.93,1.04]} & 0.80 & \scriptsize\textcolor{gray!60}{[0.80,0.81]} \\
 & Fibonacci & 0.83 & \scriptsize\textcolor{gray!60}{[0.82,0.83]} & 1.41 & \scriptsize\textcolor{gray!60}{[1.40,1.41]} & 1.08 & \scriptsize\textcolor{gray!60}{[1.07,1.08]} & 0.82 & \scriptsize\textcolor{gray!60}{[0.82,0.83]} & 1.40 & \scriptsize\textcolor{gray!60}{[1.40,1.41]} & 1.07 & \scriptsize\textcolor{gray!60}{[1.07,1.08]} \\
 & FieldLoop & 0.94 & \scriptsize\textcolor{gray!60}{[0.94,0.95]} & 1.20 & \scriptsize\textcolor{gray!60}{[1.20,1.21]} & 1.07 & \scriptsize\textcolor{gray!60}{[1.07,1.08]} & 0.94 & \scriptsize\textcolor{gray!60}{[0.93,0.94]} & 1.20 & \scriptsize\textcolor{gray!60}{[1.19,1.21]} & 1.07 & \scriptsize\textcolor{gray!60}{[1.06,1.07]} \\
 & GraphSearch & 0.31 & \scriptsize\textcolor{gray!60}{[0.30,0.31]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.43,0.44]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.38,0.39]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} & 0.41 & \scriptsize\textcolor{gray!60}{[0.40,0.42]} & 0.37 & \scriptsize\textcolor{gray!60}{[0.37,0.38]} \\
 & IntegerLoop & 0.52 & \scriptsize\textcolor{gray!60}{[0.51,0.53]} & 0.84 & \scriptsize\textcolor{gray!60}{[0.84,0.84]} & 0.67 & \scriptsize\textcolor{gray!60}{[0.66,0.67]} & 0.52 & \scriptsize\textcolor{gray!60}{[0.51,0.52]} & 0.83 & \scriptsize\textcolor{gray!60}{[0.83,0.84]} & 0.66 & \scriptsize\textcolor{gray!60}{[0.66,0.67]} \\
 & JsonSmall & 0.86 & \scriptsize\textcolor{gray!60}{[0.85,0.86]} & 1.22 & \scriptsize\textcolor{gray!60}{[1.22,1.23]} & 1.10 & \scriptsize\textcolor{gray!60}{[1.10,1.11]} & 0.85 & \scriptsize\textcolor{gray!60}{[0.84,0.85]} & 1.21 & \scriptsize\textcolor{gray!60}{[1.20,1.21]} & 1.10 & \scriptsize\textcolor{gray!60}{[1.09,1.10]} \\
 & List & 0.38 & \scriptsize\textcolor{gray!60}{[0.38,0.39]} & 0.53 & \scriptsize\textcolor{gray!60}{[0.52,0.54]} & 0.48 & \scriptsize\textcolor{gray!60}{[0.47,0.48]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.37,0.38]} & 0.52 & \scriptsize\textcolor{gray!60}{[0.52,0.53]} & 0.47 & \scriptsize\textcolor{gray!60}{[0.47,0.48]} \\
 & Loop & 0.53 & \scriptsize\textcolor{gray!60}{[0.52,0.53]} & 0.86 & \scriptsize\textcolor{gray!60}{[0.84,0.87]} & 0.70 & \scriptsize\textcolor{gray!60}{[0.70,0.71]} & 0.52 & \scriptsize\textcolor{gray!60}{[0.52,0.53]} & 0.85 & \scriptsize\textcolor{gray!60}{[0.84,0.86]} & 0.70 & \scriptsize\textcolor{gray!60}{[0.70,0.70]} \\
 & Mandelbrot & 0.46 & \scriptsize\textcolor{gray!60}{[0.45,0.46]} & 0.69 & \scriptsize\textcolor{gray!60}{[0.68,0.70]} & 0.57 & \scriptsize\textcolor{gray!60}{[0.57,0.57]} & 0.45 & \scriptsize\textcolor{gray!60}{[0.45,0.46]} & 0.69 & \scriptsize\textcolor{gray!60}{[0.68,0.70]} & 0.57 & \scriptsize\textcolor{gray!60}{[0.56,0.57]} \\
 & NBody & 0.31 & \scriptsize\textcolor{gray!60}{[0.31,0.31]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.38,0.39]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.34,0.34]} & 0.31 & \scriptsize\textcolor{gray!60}{[0.30,0.31]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.37,0.38]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.33,0.34]} \\
 & PageRank & 0.31 & \scriptsize\textcolor{gray!60}{[0.31,0.31]} & 0.44 & \scriptsize\textcolor{gray!60}{[0.43,0.44]} & 0.39 & \scriptsize\textcolor{gray!60}{[0.38,0.39]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.30,0.30]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.43,0.44]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.38,0.39]} \\
 & Permute & 0.67 & \scriptsize\textcolor{gray!60}{[0.66,0.67]} & 0.90 & \scriptsize\textcolor{gray!60}{[0.88,0.91]} & 0.82 & \scriptsize\textcolor{gray!60}{[0.82,0.82]} & 0.66 & \scriptsize\textcolor{gray!60}{[0.66,0.66]} & 0.89 & \scriptsize\textcolor{gray!60}{[0.87,0.91]} & 0.82 & \scriptsize\textcolor{gray!60}{[0.81,0.82]} \\
 & Queens & 0.77 & \scriptsize\textcolor{gray!60}{[0.77,0.78]} & 1.18 & \scriptsize\textcolor{gray!60}{[1.16,1.21]} & 0.98 & \scriptsize\textcolor{gray!60}{[0.97,0.98]} & 0.77 & \scriptsize\textcolor{gray!60}{[0.76,0.77]} & 1.18 & \scriptsize\textcolor{gray!60}{[1.16,1.20]} & 0.97 & \scriptsize\textcolor{gray!60}{[0.97,0.98]} \\
 & QuickSort & 0.98 & \scriptsize\textcolor{gray!60}{[0.98,0.98]} & 1.27 & \scriptsize\textcolor{gray!60}{[1.26,1.29]} & 1.26 & \scriptsize\textcolor{gray!60}{[1.26,1.27]} & 0.98 & \scriptsize\textcolor{gray!60}{[0.97,0.98]} & 1.26 & \scriptsize\textcolor{gray!60}{[1.25,1.28]} & 1.26 & \scriptsize\textcolor{gray!60}{[1.26,1.27]} \\
 & Recurse & 0.60 & \scriptsize\textcolor{gray!60}{[0.59,0.60]} & 0.92 & \scriptsize\textcolor{gray!60}{[0.92,0.92]} & 0.79 & \scriptsize\textcolor{gray!60}{[0.79,0.80]} & 0.60 & \scriptsize\textcolor{gray!60}{[0.59,0.60]} & 0.91 & \scriptsize\textcolor{gray!60}{[0.91,0.92]} & 0.79 & \scriptsize\textcolor{gray!60}{[0.79,0.79]} \\
 & Richards & 2.48 & \scriptsize\textcolor{gray!60}{[2.46,2.49]} & 3.72 & \scriptsize\textcolor{gray!60}{[3.61,3.83]} & 3.13 & \scriptsize\textcolor{gray!60}{[3.12,3.14]} & 2.47 & \scriptsize\textcolor{gray!60}{[2.46,2.49]} & 3.72 & \scriptsize\textcolor{gray!60}{[3.61,3.82]} & 3.13 & \scriptsize\textcolor{gray!60}{[3.12,3.14]} \\
 & Sieve & 0.67 & \scriptsize\textcolor{gray!60}{[0.66,0.67]} & 0.94 & \scriptsize\textcolor{gray!60}{[0.94,0.95]} & 0.87 & \scriptsize\textcolor{gray!60}{[0.87,0.88]} & 0.66 & \scriptsize\textcolor{gray!60}{[0.66,0.67]} & 0.94 & \scriptsize\textcolor{gray!60}{[0.93,0.94]} & 0.87 & \scriptsize\textcolor{gray!60}{[0.86,0.87]} \\
 & Storage & 0.56 & \scriptsize\textcolor{gray!60}{[0.55,0.56]} & 0.70 & \scriptsize\textcolor{gray!60}{[0.69,0.71]} & 0.69 & \scriptsize\textcolor{gray!60}{[0.69,0.69]} & 0.55 & \scriptsize\textcolor{gray!60}{[0.55,0.56]} & 0.69 & \scriptsize\textcolor{gray!60}{[0.68,0.69]} & 0.68 & \scriptsize\textcolor{gray!60}{[0.68,0.69]} \\
 & Sum & 0.52 & \scriptsize\textcolor{gray!60}{[0.52,0.53]} & 0.83 & \scriptsize\textcolor{gray!60}{[0.81,0.84]} & 0.67 & \scriptsize\textcolor{gray!60}{[0.67,0.68]} & 0.52 & \scriptsize\textcolor{gray!60}{[0.51,0.52]} & 0.82 & \scriptsize\textcolor{gray!60}{[0.81,0.83]} & 0.67 & \scriptsize\textcolor{gray!60}{[0.66,0.67]} \\
 & Towers & 0.31 & \scriptsize\textcolor{gray!60}{[0.31,0.31]} & 0.46 & \scriptsize\textcolor{gray!60}{[0.45,0.47]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.38,0.39]} & 0.31 & \scriptsize\textcolor{gray!60}{[0.30,0.31]} & 0.46 & \scriptsize\textcolor{gray!60}{[0.45,0.46]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.37,0.38]} \\
 & TreeSort & 0.32 & \scriptsize\textcolor{gray!60}{[0.31,0.32]} & 0.41 & \scriptsize\textcolor{gray!60}{[0.41,0.42]} & 0.40 & \scriptsize\textcolor{gray!60}{[0.40,0.40]} & 0.31 & \scriptsize\textcolor{gray!60}{[0.31,0.32]} & 0.40 & \scriptsize\textcolor{gray!60}{[0.39,0.40]} & 0.40 & \scriptsize\textcolor{gray!60}{[0.39,0.40]} \\
 & WhileLoop & 0.48 & \scriptsize\textcolor{gray!60}{[0.47,0.48]} & 0.72 & \scriptsize\textcolor{gray!60}{[0.72,0.73]} & 0.60 & \scriptsize\textcolor{gray!60}{[0.59,0.60]} & 0.47 & \scriptsize\textcolor{gray!60}{[0.47,0.48]} & 0.72 & \scriptsize\textcolor{gray!60}{[0.72,0.72]} & 0.59 & \scriptsize\textcolor{gray!60}{[0.59,0.60]} \\
\midrule
\multirow{26}{*}{\rotatebox{90}{som-rs-bc}} & Bounce & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.28,0.29]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.28,0.28]} & 0.29 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} \\
 & BubbleSort & 0.23 & \scriptsize\textcolor{gray!60}{[0.23,0.23]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.27,0.28]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.22]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.27,0.27]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} \\
 & DeltaBlue & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.34,0.35]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.35,0.36]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} & 0.34 & \scriptsize\textcolor{gray!60}{[0.33,0.34]} & 0.35 & \scriptsize\textcolor{gray!60}{[0.35,0.36]} \\
 & Dispatch & 0.25 & \scriptsize\textcolor{gray!60}{[0.25,0.25]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.28,0.29]} & 0.29 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} & 0.24 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.28,0.28]} & 0.29 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} \\
 & Fannkuch & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.29 & \scriptsize\textcolor{gray!60}{[0.29,0.29]} & 0.29 & \scriptsize\textcolor{gray!60}{[0.28,0.29]} & 0.24 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.28,0.29]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.28,0.28]} \\
 & Fibonacci & 0.30 & \scriptsize\textcolor{gray!60}{[0.30,0.31]} & 0.37 & \scriptsize\textcolor{gray!60}{[0.36,0.37]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.36,0.37]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.30]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.36,0.37]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.35,0.36]} \\
 & FieldLoop & 0.49 & \scriptsize\textcolor{gray!60}{[0.48,0.49]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.42,0.43]} & 0.54 & \scriptsize\textcolor{gray!60}{[0.53,0.55]} & 0.48 & \scriptsize\textcolor{gray!60}{[0.48,0.49]} & 0.42 & \scriptsize\textcolor{gray!60}{[0.42,0.43]} & 0.53 & \scriptsize\textcolor{gray!60}{[0.52,0.54]} \\
 & GraphSearch & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.12]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.14,0.15]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.11,0.12]} & 0.11 & \scriptsize\textcolor{gray!60}{[0.11,0.11]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.14]} \\
 & IntegerLoop & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.22]} & 0.24 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.26,0.26]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.21,0.22]} & 0.24 & \scriptsize\textcolor{gray!60}{[0.24,0.24]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.26,0.26]} \\
 & JsonSmall & 0.37 & \scriptsize\textcolor{gray!60}{[0.36,0.37]} & 0.39 & \scriptsize\textcolor{gray!60}{[0.39,0.40]} & 0.44 & \scriptsize\textcolor{gray!60}{[0.44,0.44]} & 0.36 & \scriptsize\textcolor{gray!60}{[0.36,0.37]} & 0.39 & \scriptsize\textcolor{gray!60}{[0.38,0.39]} & 0.44 & \scriptsize\textcolor{gray!60}{[0.43,0.44]} \\
 & List & 0.18 & \scriptsize\textcolor{gray!60}{[0.17,0.18]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.23]} & 0.21 & \scriptsize\textcolor{gray!60}{[0.20,0.21]} & 0.17 & \scriptsize\textcolor{gray!60}{[0.17,0.18]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.22]} & 0.21 & \scriptsize\textcolor{gray!60}{[0.20,0.21]} \\
 & Loop & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.23]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.25,0.26]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.21,0.22]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} \\
 & Mandelbrot & 0.20 & \scriptsize\textcolor{gray!60}{[0.19,0.20]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.21,0.22]} & 0.23 & \scriptsize\textcolor{gray!60}{[0.23,0.24]} & 0.19 & \scriptsize\textcolor{gray!60}{[0.19,0.19]} & 0.21 & \scriptsize\textcolor{gray!60}{[0.20,0.22]} & 0.23 & \scriptsize\textcolor{gray!60}{[0.23,0.23]} \\
 & NBody & 0.11 & \scriptsize\textcolor{gray!60}{[0.11,0.12]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.12]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.11 & \scriptsize\textcolor{gray!60}{[0.11,0.11]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.11,0.12]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} \\
 & PageRank & 0.13 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.13,0.13]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.14,0.15]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.12]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.13,0.14]} \\
 & Permute & 0.24 & \scriptsize\textcolor{gray!60}{[0.23,0.24]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.27,0.27]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.27,0.27]} & 0.23 & \scriptsize\textcolor{gray!60}{[0.23,0.24]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.27,0.27]} \\
 & Queens & 0.28 & \scriptsize\textcolor{gray!60}{[0.27,0.28]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.33,0.33]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.33,0.33]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.27,0.28]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.32,0.33]} \\
 & QuickSort & 0.36 & \scriptsize\textcolor{gray!60}{[0.35,0.36]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.38,0.38]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.43,0.43]} & 0.35 & \scriptsize\textcolor{gray!60}{[0.35,0.36]} & 0.38 & \scriptsize\textcolor{gray!60}{[0.37,0.38]} & 0.42 & \scriptsize\textcolor{gray!60}{[0.42,0.43]} \\
 & Recurse & 0.25 & \scriptsize\textcolor{gray!60}{[0.25,0.26]} & 0.31 & \scriptsize\textcolor{gray!60}{[0.31,0.31]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.30,0.31]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.31 & \scriptsize\textcolor{gray!60}{[0.30,0.31]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.30,0.31]} \\
 & Richards & 0.92 & \scriptsize\textcolor{gray!60}{[0.92,0.93]} & 1.20 & \scriptsize\textcolor{gray!60}{[1.20,1.21]} & 1.10 & \scriptsize\textcolor{gray!60}{[1.10,1.11]} & 0.92 & \scriptsize\textcolor{gray!60}{[0.91,0.92]} & 1.20 & \scriptsize\textcolor{gray!60}{[1.19,1.20]} & 1.10 & \scriptsize\textcolor{gray!60}{[1.09,1.11]} \\
 & Sieve & 0.25 & \scriptsize\textcolor{gray!60}{[0.25,0.26]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.31]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.25,0.26]} & 0.30 & \scriptsize\textcolor{gray!60}{[0.29,0.31]} \\
 & Storage & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.22]} & 0.21 & \scriptsize\textcolor{gray!60}{[0.20,0.21]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.25,0.26]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.21,0.22]} & 0.20 & \scriptsize\textcolor{gray!60}{[0.20,0.21]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.25,0.25]} \\
 & Sum & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.22]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.25,0.25]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.22]} & 0.24 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.26,0.27]} \\
 & Towers & 0.13 & \scriptsize\textcolor{gray!60}{[0.12,0.13]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.14,0.15]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.15,0.15]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.12]} & 0.15 & \scriptsize\textcolor{gray!60}{[0.14,0.15]} & 0.14 & \scriptsize\textcolor{gray!60}{[0.14,0.15]} \\
 & TreeSort & 0.11 & \scriptsize\textcolor{gray!60}{[0.10,0.11]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.11,0.12]} & 0.13 & \scriptsize\textcolor{gray!60}{[0.13,0.13]} & 0.11 & \scriptsize\textcolor{gray!60}{[0.10,0.11]} & 0.11 & \scriptsize\textcolor{gray!60}{[0.11,0.12]} & 0.12 & \scriptsize\textcolor{gray!60}{[0.12,0.12]} \\
 & WhileLoop & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.22]} & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.23]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.25,0.26]} & 0.21 & \scriptsize\textcolor{gray!60}{[0.21,0.22]} & 0.22 & \scriptsize\textcolor{gray!60}{[0.22,0.23]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.25]} \\
\bottomrule
\end{tabular}

### 2025-07-16 tables/gcvs_perf_summary.tex
Add final layout of GCVS experiment appendix perf section

\begin{tabular}{l l r@{\hspace{3pt}}l r@{\hspace{3pt}}l r@{\hspace{3pt}}l r@{\hspace{3pt}}l}
\toprule
Suite & Config & \multicolumn{4}{c}{Wallclock-time} & \multicolumn{4}{c}{User-time} \\
 &  & \multicolumn{2}{c}{Time (seconds)} & \multicolumn{2}{c}{Ratio} & \multicolumn{2}{c}{Time (seconds)} & \multicolumn{2}{c}{Ratio} \\
\midrule
alacritty & RC \texttt{[jemalloc]} & 0.39 & \scriptsize\textcolor{gray!60}{[0.36,0.43]} & - &  & 0.27 & \scriptsize\textcolor{gray!60}{[0.23,0.31]} & - &  \\
 & Alloy \texttt{[default]} & 0.41 & \scriptsize\textcolor{gray!60}{[0.38,0.45]} & 1.03$\times$ & \scriptsize\textcolor{gray!60}{[0.87,1.25]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.24,0.34]} & 1.05$\times$ & \scriptsize\textcolor{gray!60}{[0.75,1.48]} \\
 & RC \texttt{[gcmalloc]} & 0.40 & \scriptsize\textcolor{gray!60}{[0.38,0.43]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.87,1.21]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.23,0.31]} & 1.01$\times$ & \scriptsize\textcolor{gray!60}{[0.72,1.35]} \\
\midrule
fd & RC \texttt{[jemalloc]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.25,0.34]} & - &  & 0.13 & \scriptsize\textcolor{gray!60}{[0.10,0.16]} & - &  \\
 & Alloy \texttt{[default]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.28,0.39]} & 1.17$\times$ & \scriptsize\textcolor{gray!60}{[0.83,1.55]} & 0.16 & \scriptsize\textcolor{gray!60}{[0.13,0.21]} & 1.29$\times$ & \scriptsize\textcolor{gray!60}{[0.81,2.15]} \\
 & RC \texttt{[gcmalloc]} & 0.31 & \scriptsize\textcolor{gray!60}{[0.27,0.35]} & 1.08$\times$ & \scriptsize\textcolor{gray!60}{[0.80,1.41]} & 0.16 & \scriptsize\textcolor{gray!60}{[0.12,0.19]} & 1.21$\times$ & \scriptsize\textcolor{gray!60}{[0.77,1.93]} \\
\midrule
grmtools & RC \texttt{[jemalloc]} & 2.89 & \scriptsize\textcolor{gray!60}{[2.82,2.97]} & - &  & 2.77 & \scriptsize\textcolor{gray!60}{[2.70,2.85]} & - &  \\
 & Alloy \texttt{[default]} & 2.95 & \scriptsize\textcolor{gray!60}{[2.87,3.02]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.97,1.07]} & 2.81 & \scriptsize\textcolor{gray!60}{[2.74,2.86]} & 1.01$\times$ & \scriptsize\textcolor{gray!60}{[0.96,1.06]} \\
 & RC \texttt{[gcmalloc]} & 3.10 & \scriptsize\textcolor{gray!60}{[3.01,3.18]} & 1.07$\times$ & \scriptsize\textcolor{gray!60}{[1.01,1.13]} & 2.98 & \scriptsize\textcolor{gray!60}{[2.91,3.07]} & 1.08$\times$ & \scriptsize\textcolor{gray!60}{[1.02,1.14]} \\
\midrule
ripgrep & RC \texttt{[jemalloc]} & 1.43 & \scriptsize\textcolor{gray!60}{[1.36,1.51]} & - &  & 0.51 & \scriptsize\textcolor{gray!60}{[0.47,0.56]} & - &  \\
 & Alloy \texttt{[default]} & 1.54 & \scriptsize\textcolor{gray!60}{[1.47,1.62]} & 1.08$\times$ & \scriptsize\textcolor{gray!60}{[0.97,1.19]} & 0.62 & \scriptsize\textcolor{gray!60}{[0.57,0.68]} & 1.21$\times$ & \scriptsize\textcolor{gray!60}{[1.03,1.45]} \\
 & RC \texttt{[gcmalloc]} & 1.46 & \scriptsize\textcolor{gray!60}{[1.39,1.53]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.92,1.12]} & 0.54 & \scriptsize\textcolor{gray!60}{[0.49,0.58]} & 1.04$\times$ & \scriptsize\textcolor{gray!60}{[0.88,1.24]} \\
\midrule
som-rs-ast & RC \texttt{[jemalloc]} & 0.58 & \scriptsize\textcolor{gray!60}{[0.56,0.60]} & - &  & 0.57 & \scriptsize\textcolor{gray!60}{[0.55,0.60]} & - &  \\
 & Alloy \texttt{[default]} & 0.84 & \scriptsize\textcolor{gray!60}{[0.81,0.88]} & 1.46$\times$ & \scriptsize\textcolor{gray!60}{[1.34,1.56]} & 0.83 & \scriptsize\textcolor{gray!60}{[0.80,0.87]} & 1.45$\times$ & \scriptsize\textcolor{gray!60}{[1.34,1.58]} \\
 & RC \texttt{[gcmalloc]} & 0.73 & \scriptsize\textcolor{gray!60}{[0.70,0.75]} & 1.26$\times$ & \scriptsize\textcolor{gray!60}{[1.15,1.34]} & 0.72 & \scriptsize\textcolor{gray!60}{[0.70,0.75]} & 1.26$\times$ & \scriptsize\textcolor{gray!60}{[1.17,1.37]} \\
\midrule
som-rs-bc & RC \texttt{[jemalloc]} & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.24]} & - &  & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.24]} & - &  \\
 & Alloy \texttt{[default]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.25,0.27]} & 1.11$\times$ & \scriptsize\textcolor{gray!60}{[1.03,1.19]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.26]} & 1.11$\times$ & \scriptsize\textcolor{gray!60}{[1.03,1.20]} \\
 & RC \texttt{[gcmalloc]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.29]} & 1.18$\times$ & \scriptsize\textcolor{gray!60}{[1.10,1.28]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.28]} & 1.18$\times$ & \scriptsize\textcolor{gray!60}{[1.09,1.29]} \\
\midrule
overall & RC \texttt{[jemalloc]} & 0.49 & \scriptsize\textcolor{gray!60}{[0.47,0.51]} & - &  & 0.37 & \scriptsize\textcolor{gray!60}{[0.35,0.39]} & - &  \\
 & Alloy \texttt{[default]} & 0.58 & \scriptsize\textcolor{gray!60}{[0.56,0.61]} & 1.19$\times$ & \scriptsize\textcolor{gray!60}{[1.11,1.30]} & 0.45 & \scriptsize\textcolor{gray!60}{[0.43,0.47]} & 1.22$\times$ & \scriptsize\textcolor{gray!60}{[1.10,1.32]} \\
 & RC \texttt{[gcmalloc]} & 0.56 & \scriptsize\textcolor{gray!60}{[0.53,0.58]} & 1.14$\times$ & \scriptsize\textcolor{gray!60}{[1.05,1.24]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.41,0.45]} & 1.16$\times$ & \scriptsize\textcolor{gray!60}{[1.05,1.27]} \\
\bottomrule
\end{tabular}

### 2025-07-18 tables/elision_finalizer_counts.tex
Restructure Evaluation section and add additional plots

\begin{tabular}{l r@{\hspace{3pt}}l r@{\hspace{3pt}}l r@{\hspace{3pt}}l}
\toprule
Suite & \multicolumn{2}{c}{Time in GC} & \multicolumn{2}{c}{Wall-clock} & \multicolumn{2}{c}{User-time} \\
\midrule
alacritty & 1.01$\times$ & \scriptsize\textcolor{gray!60}{[0.90,1.14]} & 1.01$\times$ & \scriptsize\textcolor{gray!60}{[0.84,1.24]} & 1.00$\times$ & \scriptsize\textcolor{gray!60}{[0.74,1.36]} \\
fd & 1.01$\times$ & \scriptsize\textcolor{gray!60}{[0.75,1.38]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.75,1.47]} & 0.97$\times$ & \scriptsize\textcolor{gray!60}{[0.53,1.62]} \\
grmtools & 0.14$\times$ & \scriptsize\textcolor{gray!60}{[0.11,0.17]} & 0.67$\times$ & \scriptsize\textcolor{gray!60}{[0.64,0.69]} & 0.54$\times$ & \scriptsize\textcolor{gray!60}{[0.52,0.56]} \\
ripgrep & 0.47$\times$ & \scriptsize\textcolor{gray!60}{[0.43,0.56]} & 0.95$\times$ & \scriptsize\textcolor{gray!60}{[0.87,1.03]} & 0.87$\times$ & \scriptsize\textcolor{gray!60}{[0.75,1.00]} \\
som-rs-ast & 0.13$\times$ & \scriptsize\textcolor{gray!60}{[0.08,0.23]} & 0.13$\times$ & \scriptsize\textcolor{gray!60}{[0.12,0.15]} & 0.09$\times$ & \scriptsize\textcolor{gray!60}{[0.08,0.10]} \\
som-rs-bc & 0.08$\times$ & \scriptsize\textcolor{gray!60}{[0.05,0.14]} & 0.09$\times$ & \scriptsize\textcolor{gray!60}{[0.09,0.10]} & 0.07$\times$ & \scriptsize\textcolor{gray!60}{[0.06,0.07]} \\
\midrule
overall & 0.98$\times$ & \scriptsize\textcolor{gray!60}{[0.75,1.31]} & 0.26$\times$ & \scriptsize\textcolor{gray!60}{[0.24,0.28]} & 0.20$\times$ & \scriptsize\textcolor{gray!60}{[0.18,0.23]} \\
\bottomrule
\end{tabular}

### 2025-07-27 response.tex
Flesh out an author response

\documentclass[12pt,a4paper,preprint]{article}

\usepackage{setspace}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{softdev}
\usepackage{quoting}
\usepackage{xspace}
\usepackage[many]{tcolorbox}
\newtcolorbox{blockquote}{%
  sharp corners,
  colback=gray!5,
  colframe=gray!60,
  leftrule=2pt,
  enhanced,
  before skip=6pt, after skip=18pt,
  boxrule=0pt,
  left=6pt, right=4pt,
  borderline west={2pt}{0pt}{gray!60},
  fontupper=\scriptsize\sffamily\selectfont
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2.0ex plus0.5ex minus0.2ex}

%\newcommand\laurie[1]{\mynote{Laurie}{#1}}
%\newcommand\jake[1]{\mynote{Jake}{#1}}

\newcommand\Egcrc{E$_\textrm{gcvs}$\xspace}
\newcommand\Eelision{E$_\textrm{elision}$\xspace}
\newcommand\Epremopt{E$_\textrm{premopt}$\xspace}

\begin{document}

\date{}  % This removes the date
\title{Response to Reviewer Feedback}
\maketitle

We thank the reviewers for their thoughtful reviews! While our \texttt{revisions R2} submission contains a PDF diff that shows prose modifications, we recognize that many review comments centered on our evaluation approach. Since \texttt{latexdiff} cannot effectively display changes to figures and tables, this document serves as a brief guide to our major revisions.

Below, we highlight the most significant changes made in response to reviewer input, including references to new visualizations that directly address the points raised during review.

\subsection*{Better Justification around Finalizers}

\begin{blockquote}
explicitly discuss and present the issues around finalizations semantics, as learned from other languages...\\

... This should take the form of a) explicit acknowledgement of the issue of this as a solution (as per the JEP) b) explain why such an undesirable solution is unavoidable (if it is) c) clearly explain how the problems with finalization semantics relate to destructor semantics which Rust has already bought into (i.e. exactly how much introducing this approach makes things worse or not).
\end{blockquote}

We have updated Section 4.1 to include a more detailed discussion of how finalization semantics relate to destructor semantics in Rust in particular. We offer a concrete example of an instance where finalizers can actually lead to more drop methods being run than their equivalent destructor based counterparts -- across panic unwind boundaries on different mutator threads.

We also update Section 4.2 to more explicitly address finalizer challenges (such as latency) as they relate to JEP-421.

In Section 4 we mention that despite the issues surrounding finalization, Rust's heavy reliance on destructor-based code, and Alloy's desire allow GC interaction with these objects, finalization is inevitable.

\subsection*{Performance Evaluation}

\begin{blockquote}
include the non-BDW baseline in the evaluation and discuss the utility of this approach w.r.t. that performance result. Ideally this would include a discussion of how much of the performance deficit is likely redeemable via "engineering", and how much is likely to be intrinsic (i.e. due to unavoidable conservatism), so that we can get a better intuition of the plausible "best case" for this approach.
\end{blockquote}

We have standardized all visualizations in Section 8 by normalizing against
appropriate baselines. Each experiment uses a specific baseline for comparison:
non-BDW allocator benchmarks for the \Egcrc experiment (RC comparison)
\jake{TODO link to figures}, naive Alloy without elision for the \Eelision
experiment \jake{TODO link to figures}, and barrier-free execution for the
\Epremopt experiment \jake{TODO link to figures}. All results are presented as
ratio relative to these baselines rather than raw values. For the interested
reader, we provide the raw values for each experiment in appendix tables.

We offer a discussion of the engineering cost in the prose in section \jake{TODO: section}

\subsection*{Conclusion}

\begin{blockquote}
add a discussion thats sums up the overall benefits/drawbacks of this particular approach, possibly depending on specific scenarios/use cases, and perhaps outlines directions for future work from a conceptional perspective, i.e., possible design directions that could be investigated
\end{blockquote}

\end{document}

### 2025-07-27 response.tex
Wrap lines.
No changes to content, but without wrapped lines, diffs become a
nightmare.

@@
 
-We thank the reviewers for their thoughtful reviews!
-While our \texttt{revisions R2} submission contains a PDF diff that shows prose modifications, we recognize that many review comments centered on our evaluation approach.
-Since \texttt{latexdiff} cannot effectively display changes to figures and tables, this document serves as a brief guide to our major revisions.
+We thank the reviewers for their thoughtful reviews! While our
+\texttt{revisions R2} submission contains a PDF diff that shows prose
+modifications, we recognize that many review comments centered on our
+evaluation approach. Since \texttt{latexdiff} cannot effectively display
+changes to figures and tables, this document serves as a brief guide to our
+major revisions.
 
-Below, we highlight the most significant changes made in response to reviewer input, including references to new visualizations that directly address the points raised during review.
+Below, we highlight the most significant changes made in response to reviewer
+input, including references to new visualizations that directly address the
+points raised during review.
 
@@
 
-\begin{blockquote}
-explicitly discuss and present the issues around finalizations semantics, as learned from other languages...\\
+\begin{blockquote} explicitly discuss and present the issues around
+  finalizations semantics, as learned from other languages...\\
 
-...
-This should take the form of a) explicit acknowledgement of the issue of this as a solution (as per the JEP) b) explain why such an undesirable solution is unavoidable (if it is) c) clearly explain how the problems with finalization semantics relate to destructor semantics which Rust has already bought into (i.e.
-exactly how much introducing this approach makes things worse or not).
+... This should take the form of a) explicit acknowledgement of the issue of
+this as a solution (as per the JEP) b) explain why such an undesirable solution
+is unavoidable (if it is) c) clearly explain how the problems with finalization
+semantics relate to destructor semantics which Rust has already bought into
+(i.e. exactly how much introducing this approach makes things worse or not).
 \end{blockquote}
 
-We have updated Section 4.1 to include a more detailed discussion of how finalization semantics relate to destructor semantics in Rust in particular.
-We offer a concrete example of an instance where finalizers can actually lead to more drop methods being run than their equivalent destructor based counterparts -- across panic unwind boundaries on different mutator threads.
+We have updated Section 4.1 to include a more detailed discussion of how
+finalization semantics relate to destructor semantics in Rust in particular. We
+offer a concrete example of an instance where finalizers can actually lead to
+more drop methods being run than their equivalent destructor based counterparts
+-- across panic unwind boundaries on different mutator threads.
 
-We also update Section 4.2 to more explicitly address finalizer challenges (such as latency) as they relate to JEP-421.
+We also update Section 4.2 to more explicitly address finalizer challenges
+(such as latency) as they relate to JEP-421.
 
-In Section 4 we mention that despite the issues surrounding finalization, Rust's heavy reliance on destructor-based code, and Alloy's desire allow GC interaction with these objects, finalization is inevitable.
+In Section 4 we mention that despite the issues surrounding finalization,
+Rust's heavy reliance on destructor-based code, and Alloy's desire allow GC
+interaction with these objects, finalization is inevitable.
 
@@
 \begin{blockquote}
-include the non-BDW baseline in the evaluation and discuss the utility of this approach w.r.t.
-that performance result.
-Ideally this would include a discussion of how much of the performance deficit is likely redeemable via "engineering", and how much is likely to be intrinsic (i.e.
-due to unavoidable conservatism), so that we can get a better intuition of the plausible "best case" for this approach.
+include the non-BDW baseline in the evaluation and discuss the utility of this
+approach w.r.t. that performance result. Ideally this would include a
+discussion of how much of the performance deficit is likely redeemable via
+"engineering", and how much is likely to be intrinsic (i.e. due to
+unavoidable conservatism), so that we can get a better intuition of the
+plausible "best case" for this approach.
 \end{blockquote}
@@
 \begin{blockquote}
-add a discussion thats sums up the overall benefits/drawbacks of this particular approach, possibly depending on specific scenarios/use cases, and perhaps outlines directions for future work from a conceptional perspective, i.e., possible design directions that could be investigated
+add a discussion thats sums up the overall benefits/drawbacks of this
+particular approach, possibly depending on specific scenarios/use cases, and
+perhaps outlines directions for future work from a conceptional perspective,
+i.e., possible design directions that could be investigated
 \end{blockquote}

### 2025-07-27 response.tex
Edit the response.

@@
 \usepackage{amssymb}
+\usepackage{listings}
+\usepackage{listings-rust}
 \usepackage{softdev}
@@
 \newcommand\Epremopt{E$_\textrm{premopt}$\xspace}
+\newcommand\boehm{\textsc{BDWGC}\xspace}
 
@@
 
-We thank the reviewers for their thoughtful reviews! While our
-\texttt{revisions R2} submission contains a PDF diff that shows prose
-modifications, we recognize that many review comments centered on our
-evaluation approach. Since \texttt{latexdiff} cannot effectively display
-changes to figures and tables, this document serves as a brief guide to our
-major revisions.
+We thank the reviewers for their thoughtful reviews: we hope to have
+taken onboard your feedback and addressed your questions. In this document
+we summarise the major changes we have made: the diff shows changes to the prose
+(though it does tend to mangle changes to figures and tables).
 
-Below, we highlight the most significant changes made in response to reviewer
-input, including references to new visualizations that directly address the
-points raised during review.
+\subsection*{Finalization semantics}
 
-\subsection*{Better Justification around Finalizers}
-
-\begin{blockquote} explicitly discuss and present the issues around
-  finalizations semantics, as learned from other languages...\\
-
-... This should take the form of a) explicit acknowledgement of the issue of
-this as a solution (as per the JEP) b) explain why such an undesirable solution
-is unavoidable (if it is) c) clearly explain how the problems with finalization
-semantics relate to destructor semantics which Rust has already bought into
-(i.e. exactly how much introducing this approach makes things worse or not).
+\begin{blockquote}
+explicitly discuss and present the issues around finalizations semantics, as
+  learned from other languages
 \end{blockquote}
 
-We have updated Section 4.1 to include a more detailed discussion of how
-finalization semantics relate to destructor semantics in Rust in particular. We
-offer a concrete example of an instance where finalizers can actually lead to
-more drop methods being run than their equivalent destructor based counterparts
--- across panic unwind boundaries on different mutator threads.
+We have made a number of changes (chiefly to the end of Section 3, and
+throughout Section 4), which we hope address this.
 
-We also update Section 4.2 to more explicitly address finalizer challenges
-(such as latency) as they relate to JEP-421.
+As the reviewers note ``an
+implementation that does not finalize anything would be compliant when
+finalization may be deferred indefinitely'' is true of most GCed
+implementations we are aware of, including Java. Indeed, Java once had the
+\lstinline{runFinalizersOnExit} flag to force finalizers to be run before the
+JVM exists, but it is marked as deprecated as ``inherently unsafe''; instead,
+there is now the \lstinline{addShutdownHook} mechanism.
 
-In Section 4 we mention that despite the issues surrounding finalization,
-Rust's heavy reliance on destructor-based code, and Alloy's desire allow GC
-interaction with these objects, finalization is inevitable.
+While investigating thus further, we discovered one surprise (to us, at least),
+which muddies the waters with respect to finalizer latency further. In Rust,
+when a thread unwinds (i.e.~panics) then, depending on compile-time flags, no
+destructors will be run --- but Alloy can run all of the `queued' finalizers!
+We have not belaboured this point in the paper, but it shows that destructors
+can have guaranteed-infinite latency in some situations where finalizers have
+infinite-at-worst latency.
 
@@
 
+We have made a large number of changes to the performance evaluation. These are
+mostly due to reviewer comments, but we also uncovered two mistakes in our
+experiment: (1) we used metric XYZ instead of ABC in \boehm (2) we incorrectly
+calculated confidence intervals in \laurie{which cases?}. While neither mistake
+fundamentally changes the outcome, we believe it is important that we not
+try and sweep this under the carpet.
+
+The most significant changes are:
+
+\begin{itemize}
+  \item We provide a comparison of \lstinline{Rc<T>} with jemalloc and \boehm
+    in Table~\laurie{3?} in the Appendix. This suggests that the inherent
+    overhead of \boehm ranges from 2--26\%, averaging around 11\%.
+
+  \item We have standardized all visualizations by normalizing against
+    appropriate baselines (e.g.~Alloy-without-elision as the baseline for
+    the \Eelision experiment; and barrier-free execution as the baseline
+    for the \Epremopt experiment). This allows us to show what we hope
+    are easily understand performance ratios. We also provide the raw data
+    in the appendix.
+
+  \item We provide data for wall-clock and user-time.
+\end{itemize}
+
+The downside to this is that we now present far too many figures and tables to
+fit in the main body of the paper! We have tried to select the subset of
+visualizations that will most quickly help the reader understand the overall
+picture for the main body of the paper, relegating everything else to the
+appendix.
+
+We were asked -- when explaining the overhead of \boehm -- the following:
+
 \begin{blockquote}
-include the non-BDW baseline in the evaluation and discuss the utility of this
-approach w.r.t. that performance result. Ideally this would include a
+Ideally this would include a
 discussion of how much of the performance deficit is likely redeemable via
@@
 
-We have standardized all visualizations in Section 8 by normalizing against
-appropriate baselines. Each experiment uses a specific baseline for comparison:
-non-BDW allocator benchmarks for the \Egcrc experiment (RC comparison)
-\jake{TODO link to figures}, naive Alloy without elision for the \Eelision
-experiment \jake{TODO link to figures}, and barrier-free execution for the
-\Epremopt experiment \jake{TODO link to figures}. All results are presented as
-ratio relative to these baselines rather than raw values. For the interested
-reader, we provide the raw values for each experiment in appendix tables.
-
-We offer a discussion of the engineering cost in the prose in section \jake{TODO: section}
+Although we can now quantify the overhead of Boehm vs.~jemalloc in our context,
+the data doesn't really give us clues as to why the overhead exists. That makes
+us nervous about speculating further. While we are not total allocator dummies,
+both of us have talked to allocator experts over the years to know that there is a lot
+here that we don't know. At a high level, \boehm is -- and we don't mean this as an
+insult or criticism! -- ``old''. Since then many allocators (e.g.~dlmalloc, jemalloc)
+have been designed, and subsequently tweaked and improved; each such allocator
+is full of many decisions which are likely to affect its performance. Unfortunately,
+we don't really know which decisions might be relevant or not.
 
@@
 
+We have expanded the conclusions, but we hope to have done so in a way
+that does not overstate our confidence in our predictions.
+
 \end{document}

### 2025-07-28 response.tex
Add some detailed comments to the response

@@
 
-While investigating thus further, we discovered one surprise (to us, at least),
+While investigating this further, we discovered one surprise (to us, at least),
 which muddies the waters with respect to finalizer latency further. In Rust,
@@
 
+\jake{Since the original submission, alloy has been updated. We now
+dynamically link boehm in all cases. For memory metrics, this alone won't
+change things because we always used dynamic linkage for these tests anyway.
+However, this may have affected wall-clock performance on some individual
+benchmarks (though it's really hard to tell which, because there are
+confounders: we also now run benchmarks on b15; we made changes to finalization
+based on Andy wingo's feedback (mentioned below); and we made a couple of other
+unrelated QoL and implementation changes to Alloy (i doubt these made a
+difference, but who knows). What is clear though is that even if individual
+benchmarks may have changed, the overall picture has not not since original
+submission.}
+
 We have made a large number of changes to the performance evaluation. These are
-mostly due to reviewer comments, but we also uncovered two mistakes in our
-experiment: (1) we used metric XYZ instead of ABC in \boehm (2) we incorrectly
-calculated confidence intervals in \laurie{which cases?}. While neither mistake
+mostly due to reviewer comments, but we also uncovered a mistake in our
+experiment. We used \boehm's \lstinline{GC_heapsize} metric (which never
+shrinks) for calculating in-use heap snapshots, we have since modified boehm to
+output the number of bytes swept and explicitly freed on each GC. While neither mistake
 fundamentally changes the outcome, we believe it is important that we not
-try and sweep this under the carpet.
+try and sweep this under the carpet. \jake{This does fundamentally change the
+memory results for finalizer elision. In som-rs-ast, som-rs-bc, grmtools, and
+ripgrep, finalizer elision now uses less memory than the no-elision
+configuration. In the original submission, we incorrectly observed that it had
+a higher average heap usage as a trade-off for better wall-clock performance.}
+\jake{furthermore, since the original submission we have changed the way that
+finalization works: we now use Boehm's \lstinline{finalize_on_demand} API based on
+Andy Wingo's feedback. It is very possible that this could have moved the dial
+on heap size too, how much that this changes things in relation to the above
+mentioned wrong metric error I don't know. but it has crossed my mind.}
 
@@
   \item We provide data for wall-clock and user-time.
+
+  \item We provide data for the number of collections run, and the total GC
+  pause time.
 \end{itemize}
@@
 
+\jake{My reading of this reviewer comment is that our mention of allocator
+differences are just a partial (yet important!) answer. I think they are also
+asking something else too (based on their mention of ``unavoidable
+conservatism''). This is more along the lines of: ``what GC-specific
+engineering would be needed to make this research-based GC productionised to
+have comparable performance with jemalloc RC''. My intuition is that they're
+wondering about things like ``what if you had a Bartlett-style
+semi-conservative collector rather than fully conservative?'' The short answer
+here would also be ``it's too difficult to say'' IMHO. Bartlett-style
+collection muddies the waters a bit showing that (counter to what I would
+assume) precise object scanning doesn't make a lot of difference in terms of
+wall-clock time. For some workloads its slower, for others its a modest
+improvement. And trying to make guesses on Rust workloads based off of this
+would be pure speculation on my part. Precise GC OTOH would be an interesting
+comparison, maybe fully moving compaction would improve things... but as we
+mention in the paper, this is not possible while respecting the Rust semantics
+of today. If you think this is worth mentioning in the body of the paper I can
+do so and include a citation to the Bartlett work. I don't know how on-topic it
+is though.}
+
 \subsection*{Conclusion}

### 2025-07-28 response.tex
Edit the response.

--- 2025-07-27 response.tex
@@
 \lstinline{runFinalizersOnExit} flag to force finalizers to be run before the
-JVM exists, but it is marked as deprecated as ``inherently unsafe''; instead,
+JVM exists; it was long marked as deprecated as ``inherently unsafe'' and
+now appears to have been removed; instead,
 there is now the \lstinline{addShutdownHook} mechanism.
 
-While investigating thus further, we discovered one surprise (to us, at least),
+While investigating this further, we discovered one surprise (to us, at least),
 which muddies the waters with respect to finalizer latency further. In Rust,
@@
 We have made a large number of changes to the performance evaluation. These are
-mostly due to reviewer comments, but we also uncovered two mistakes in our
-experiment: (1) we used metric XYZ instead of ABC in \boehm (2) we incorrectly
-calculated confidence intervals in \laurie{which cases?}. While neither mistake
-fundamentally changes the outcome, we believe it is important that we not
-try and sweep this under the carpet.
+mostly due to reviewer comments, but we also uncovered a mistake in our
+experiment. We previously used \boehm's \lstinline{GC_heapsize} metric:
+this does not, as we assumed, represent current heap usage, but total
+memory usage since the program's start. We now use the \laurie{XYZ} metric,
+which does measure the correct thing. This changes the results for finalizer
+elision in on way: previously this appeared to cause heap usage to grow, but in
+fact it shrinks.
 
@@
   \item We provide data for wall-clock and user-time.
+
+  \item We provide data for the number of collections run, and the total GC
+  pause time.
 \end{itemize}
+
+We also made some minor changes (e.g.~we now always use dynamic
+linking of \boehm; we reran benchmarks on a more modern machine), but
+these had no obvious impact on our results.
 
@@
 
+We ended up a little unsure which of two questions this might be asking,
+so please forgive us if we answer both!
+
 Although we can now quantify the overhead of Boehm vs.~jemalloc in our context,
@@
 we don't really know which decisions might be relevant or not.
+
+Another possibility is to use a Bartlett-esque semi-conservative GC. The literature
+offers a complex picture: sometimes this is faster, sometimes slower, than
+fully conservative GC. We again lack confidence to know how this might translate
+into our context.
 

### 2025-07-29 tables/exclusions.tex
Flesh out excluded benchmark appendix table

\begin{tabular}{lll}
\toprule
Benchmark         & Description                              & Reason for exclusion                                       \\
\midrule
bevy          & ECS game engine in Rust                   & \jake{TODO} \\
dyon          & Scripting language in Rust                & \jake{TODO} \\
jiff          & A datetime library for Rust               & \jake{TODO} \\
mini-moka     & Concurrent in-memory cache library        & \jake{TODO} \\
numbat        & Math search engine                        & \jake{TODO} \\
rkyv          & Zero-copy deserialization framework       & \jake{TODO} \\
RustPython    & Python interpreter written in Rust        & \jake{TODO} \\
rust-analyzer & Language server for Rust                  & \jake{TODO} \\
salsa         & Incremental recomputation library         & \jake{TODO} \\
WLambda       & scripting language in Rust                & \jake{TODO} \\
\bottomrule
\end{tabular}

### 2025-07-29 tables/exclusions.tex
Update benchmark exclusions table in appendix

@@
 \midrule
-bevy          & ECS game engine in Rust                   & \jake{TODO} \\
-dyon          & Scripting language in Rust                & \jake{TODO} \\
-jiff          & A datetime library for Rust               & \jake{TODO} \\
-mini-moka     & Concurrent in-memory cache library        & \jake{TODO} \\
-numbat        & Math search engine                        & \jake{TODO} \\
-rkyv          & Zero-copy deserialization framework       & \jake{TODO} \\
-RustPython    & Python interpreter written in Rust        & \jake{TODO} \\
-rust-analyzer & Language server for Rust                  & \jake{TODO} \\
-salsa         & Incremental recomputation library         & \jake{TODO} \\
-WLambda       & scripting language in Rust                & \jake{TODO} \\
+bevy          & ECS game engine in Rust                   & Unable to port successfully (see \cref{rustpython}) \\
+dyon          & Scripting language in Rust                & Unable to port successfully (see \cref{rustpython})\\
+jiff          & A datetime library for Rust               & Too few allocations to measure \\
+mini-moka     & Concurrent in-memory cache library        & Too few allocations to measure \\
+numbat        & Math search engine                        & Too few allocations to measure \\
+rkyv          & Zero-copy deserialization framework       & Insufficient \texttt{Gc<T>} coverage in benchmarks \\
+RustPython    & Python interpreter written in Rust        & Difficulty retro-fitting \texttt{\_\_del\_\_} semantics (see \cref{rustpython}). \\
+rust-analyzer & Language server for Rust                  & Unable to port successfully (see \cref{rustpython}) \\
+salsa         & Incremental recomputation library         & Too few allocations to measure \\
+WLambda       & Scripting language written in Rust        & Insufficient \texttt{Gc<T>} coverage in benchmarks \\
 \bottomrule

### 2025-07-30 tables/gcvs_perf_summary.tex
Remove all red and fix all todos

@@
-\begin{tabular}{l l r@{\hspace{3pt}}l r@{\hspace{3pt}}l r@{\hspace{3pt}}l r@{\hspace{3pt}}l}
+\begin{tabular}{l l r@{\hspace{3pt}}l r@{\hspace{3pt}}l}
 \toprule
-Suite & Config & \multicolumn{4}{c}{Wallclock-time} & \multicolumn{4}{c}{User-time} \\
- &  & \multicolumn{2}{c}{Time (seconds)} & \multicolumn{2}{c}{Ratio} & \multicolumn{2}{c}{Time (seconds)} & \multicolumn{2}{c}{Ratio} \\
-\midrule
-alacritty & RC \texttt{[jemalloc]} & 0.39 & \scriptsize\textcolor{gray!60}{[0.36,0.43]} & - &  & 0.27 & \scriptsize\textcolor{gray!60}{[0.23,0.31]} & - &  \\
- & Alloy \texttt{[default]} & 0.41 & \scriptsize\textcolor{gray!60}{[0.38,0.45]} & 1.03$\times$ & \scriptsize\textcolor{gray!60}{[0.87,1.25]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.24,0.34]} & 1.05$\times$ & \scriptsize\textcolor{gray!60}{[0.75,1.48]} \\
- & RC \texttt{[gcmalloc]} & 0.40 & \scriptsize\textcolor{gray!60}{[0.38,0.43]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.87,1.21]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.23,0.31]} & 1.01$\times$ & \scriptsize\textcolor{gray!60}{[0.72,1.35]} \\
-\midrule
-fd & RC \texttt{[jemalloc]} & 0.28 & \scriptsize\textcolor{gray!60}{[0.25,0.34]} & - &  & 0.13 & \scriptsize\textcolor{gray!60}{[0.10,0.16]} & - &  \\
- & Alloy \texttt{[default]} & 0.33 & \scriptsize\textcolor{gray!60}{[0.28,0.39]} & 1.17$\times$ & \scriptsize\textcolor{gray!60}{[0.83,1.55]} & 0.16 & \scriptsize\textcolor{gray!60}{[0.13,0.21]} & 1.29$\times$ & \scriptsize\textcolor{gray!60}{[0.81,2.15]} \\
- & RC \texttt{[gcmalloc]} & 0.31 & \scriptsize\textcolor{gray!60}{[0.27,0.35]} & 1.08$\times$ & \scriptsize\textcolor{gray!60}{[0.80,1.41]} & 0.16 & \scriptsize\textcolor{gray!60}{[0.12,0.19]} & 1.21$\times$ & \scriptsize\textcolor{gray!60}{[0.77,1.93]} \\
-\midrule
-grmtools & RC \texttt{[jemalloc]} & 2.89 & \scriptsize\textcolor{gray!60}{[2.82,2.97]} & - &  & 2.77 & \scriptsize\textcolor{gray!60}{[2.70,2.85]} & - &  \\
- & Alloy \texttt{[default]} & 2.95 & \scriptsize\textcolor{gray!60}{[2.87,3.02]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.97,1.07]} & 2.81 & \scriptsize\textcolor{gray!60}{[2.74,2.86]} & 1.01$\times$ & \scriptsize\textcolor{gray!60}{[0.96,1.06]} \\
- & RC \texttt{[gcmalloc]} & 3.10 & \scriptsize\textcolor{gray!60}{[3.01,3.18]} & 1.07$\times$ & \scriptsize\textcolor{gray!60}{[1.01,1.13]} & 2.98 & \scriptsize\textcolor{gray!60}{[2.91,3.07]} & 1.08$\times$ & \scriptsize\textcolor{gray!60}{[1.02,1.14]} \\
-\midrule
-ripgrep & RC \texttt{[jemalloc]} & 1.43 & \scriptsize\textcolor{gray!60}{[1.36,1.51]} & - &  & 0.51 & \scriptsize\textcolor{gray!60}{[0.47,0.56]} & - &  \\
- & Alloy \texttt{[default]} & 1.54 & \scriptsize\textcolor{gray!60}{[1.47,1.62]} & 1.08$\times$ & \scriptsize\textcolor{gray!60}{[0.97,1.19]} & 0.62 & \scriptsize\textcolor{gray!60}{[0.57,0.68]} & 1.21$\times$ & \scriptsize\textcolor{gray!60}{[1.03,1.45]} \\
- & RC \texttt{[gcmalloc]} & 1.46 & \scriptsize\textcolor{gray!60}{[1.39,1.53]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.92,1.12]} & 0.54 & \scriptsize\textcolor{gray!60}{[0.49,0.58]} & 1.04$\times$ & \scriptsize\textcolor{gray!60}{[0.88,1.24]} \\
-\midrule
-som-rs-ast & RC \texttt{[jemalloc]} & 0.58 & \scriptsize\textcolor{gray!60}{[0.56,0.60]} & - &  & 0.57 & \scriptsize\textcolor{gray!60}{[0.55,0.60]} & - &  \\
- & Alloy \texttt{[default]} & 0.84 & \scriptsize\textcolor{gray!60}{[0.81,0.88]} & 1.46$\times$ & \scriptsize\textcolor{gray!60}{[1.34,1.56]} & 0.83 & \scriptsize\textcolor{gray!60}{[0.80,0.87]} & 1.45$\times$ & \scriptsize\textcolor{gray!60}{[1.34,1.58]} \\
- & RC \texttt{[gcmalloc]} & 0.73 & \scriptsize\textcolor{gray!60}{[0.70,0.75]} & 1.26$\times$ & \scriptsize\textcolor{gray!60}{[1.15,1.34]} & 0.72 & \scriptsize\textcolor{gray!60}{[0.70,0.75]} & 1.26$\times$ & \scriptsize\textcolor{gray!60}{[1.17,1.37]} \\
-\midrule
-som-rs-bc & RC \texttt{[jemalloc]} & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.24]} & - &  & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.24]} & - &  \\
- & Alloy \texttt{[default]} & 0.26 & \scriptsize\textcolor{gray!60}{[0.25,0.27]} & 1.11$\times$ & \scriptsize\textcolor{gray!60}{[1.03,1.19]} & 0.25 & \scriptsize\textcolor{gray!60}{[0.24,0.26]} & 1.11$\times$ & \scriptsize\textcolor{gray!60}{[1.03,1.20]} \\
- & RC \texttt{[gcmalloc]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.29]} & 1.18$\times$ & \scriptsize\textcolor{gray!60}{[1.10,1.28]} & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.28]} & 1.18$\times$ & \scriptsize\textcolor{gray!60}{[1.09,1.29]} \\
-\midrule
-overall & RC \texttt{[jemalloc]} & 0.49 & \scriptsize\textcolor{gray!60}{[0.47,0.51]} & - &  & 0.37 & \scriptsize\textcolor{gray!60}{[0.35,0.39]} & - &  \\
- & Alloy \texttt{[default]} & 0.58 & \scriptsize\textcolor{gray!60}{[0.56,0.61]} & 1.19$\times$ & \scriptsize\textcolor{gray!60}{[1.11,1.30]} & 0.45 & \scriptsize\textcolor{gray!60}{[0.43,0.47]} & 1.22$\times$ & \scriptsize\textcolor{gray!60}{[1.10,1.32]} \\
- & RC \texttt{[gcmalloc]} & 0.56 & \scriptsize\textcolor{gray!60}{[0.53,0.58]} & 1.14$\times$ & \scriptsize\textcolor{gray!60}{[1.05,1.24]} & 0.43 & \scriptsize\textcolor{gray!60}{[0.41,0.45]} & 1.16$\times$ & \scriptsize\textcolor{gray!60}{[1.05,1.27]} \\
+Suite & Allocator & Wallclock time (s) & & Slowdown & \\
+\toprule
+alacritty & \texttt{jemalloc}       & 0.39 & \scriptsize\textcolor{gray!60}{[0.36,0.43]} & -           &  \\
+          & \texttt{boehm}          & 0.40 & \scriptsize\textcolor{gray!60}{[0.38,0.43]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.87,1.21]} \\[2pt]
+fd        & \texttt{jemalloc}       & 0.28 & \scriptsize\textcolor{gray!60}{[0.25,0.34]} & -           &  \\
+          & \texttt{boehm}          & 0.31 & \scriptsize\textcolor{gray!60}{[0.27,0.35]} & 1.08$\times$ & \scriptsize\textcolor{gray!60}{[0.80,1.41]} \\[2pt]
+grmtools  & \texttt{jemalloc}       & 2.89 & \scriptsize\textcolor{gray!60}{[2.82,2.97]} & -           &  \\
+          & \texttt{boehm}          & 3.10 & \scriptsize\textcolor{gray!60}{[3.01,3.18]} & 1.07$\times$ & \scriptsize\textcolor{gray!60}{[1.01,1.13]} \\[2pt]
+ripgrep   & \texttt{jemalloc}       & 1.43 & \scriptsize\textcolor{gray!60}{[1.36,1.51]} & -           &  \\
+          & \texttt{boehm}          & 1.46 & \scriptsize\textcolor{gray!60}{[1.39,1.53]} & 1.02$\times$ & \scriptsize\textcolor{gray!60}{[0.92,1.12]} \\[2pt]
+som-rs-ast & \texttt{jemalloc}      & 0.58 & \scriptsize\textcolor{gray!60}{[0.56,0.60]} & -           &  \\
+           & \texttt{boehm}         & 0.73 & \scriptsize\textcolor{gray!60}{[0.70,0.75]} & 1.26$\times$ & \scriptsize\textcolor{gray!60}{[1.15,1.34]} \\[2pt]
+som-rs-bc  & \texttt{jemalloc}      & 0.23 & \scriptsize\textcolor{gray!60}{[0.22,0.24]} & -           &  \\
+           & \texttt{boehm}         & 0.27 & \scriptsize\textcolor{gray!60}{[0.26,0.29]} & 1.18$\times$ & \scriptsize\textcolor{gray!60}{[1.10,1.28]} \\[2pt]
+overall   & \texttt{jemalloc}       & 0.49 & \scriptsize\textcolor{gray!60}{[0.47,0.51]} & -           &  \\
+          & \texttt{boehm}          & 0.56 & \scriptsize\textcolor{gray!60}{[0.53,0.58]} & 1.14$\times$ & \scriptsize\textcolor{gray!60}{[1.05,1.24]} \\
 \bottomrule

### 2025-07-30 response.tex
Update response

@@
 this does not, as we assumed, represent current heap usage, but total
-memory usage since the program's start. We now use the \laurie{XYZ} metric,
+memory usage since the program's start. We now use the \lstinline{GC_bytes_allocd} metric,
 which does measure the correct thing. This changes the results for finalizer
-elision in on way: previously this appeared to cause heap usage to grow, but in
+elision in one way: previously this appeared to cause heap usage to grow, but in
 fact it shrinks.
@@
   \item We provide a comparison of \lstinline{Rc<T>} with jemalloc and \boehm
-    in Table~\laurie{3?} in the Appendix. This suggests that the inherent
+    in Table~4 in the Appendix. This suggests that the inherent
     overhead of \boehm ranges from 2--26\%, averaging around 11\%.

### 2025-08-26 listings/first_example.rs
Fix ACM formatting issues

@@ -13,5 +13,6 @@ fn main() {
   gc2.borrow_mut().nbr = Some(gc2);
   gc1 = gc2;
   force_gc();
-  println!("{} {}", gc1.borrow().value, gc1.borrow().nbr.unwrap().borrow().value);
+  println!("{} {}", gc1.borrow().value, 
+		    gc1.borrow().nbr.unwrap().borrow().value);
 }
